\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-28 tex/ms.tex
minor fixes

For each of the two sectors considered, we downloaded a random subsample of 
1,000 short-cadence light curve files corresponding to postage stamps located 
across the full \TESS field of view and extracted the background flux time 
series (\textsf{SAP\_BKG}) and corresponding uncertainties
(\textsf{SAP\_BKG\_ERR}) from each. 
Not all postage stamps are equally informative, since the desired signal from 
Sol d is inhomogeneously spread across the \TESS detectors and manifests itself
differently in different regions (see \S\ref{sec:systematics}). 
We down-selected our pool of 1,000 targets to 75 maximally useful background 
light curves from Sector 1 and 20 from Sector 2. 
This down-selection was done with several criteria in mind: each light curve 
should contain a significant signal from Sol d; they should be representative 
of the general background flux modulation seen across the \TESS cameras, rather 
than containing any truly localized signals from astrophysical background 
sources; and the sample as a whole should contain the full range of typical 
behaviors of background across the entire \TESS field of view. 
To accomplish this, we interpolated all light curves in Sector 1 onto the same time
grid, masked all cadences with nonzero \textsf{QUALITY} flags and
cadences during which Sol d was below the edge of the sunshade.
During the selection step only, we also normalized them to the same min-max range.
We then computed the median
flux at each cadence along with an estimate of the variance based on the
median absolute deviation (MAD) across all light curves.
For each light curve, we calculated a score $\chi^2$ equal to the sum of the squares of the
deviation from the median at each of the $N$ cadences, normalized by the variance.
We removed all light curves with $\chi^2 < N$ from the pool, placing
them in a separate group. We repeated these steps several times,
classifying light curves into four groups for Sector 1 and two groups for Sector 2. 
We found that this
procedure effectively grouped together light curves with similar features,
increasing in variation within each group from the first group (most homogeneous) 
to the last group (most heterogeneous). In practice, we found light curves
in all but the last group to be dominated by 
the signal of Sol d, while light
curves in the last group were dominated by signals other than the
periodic modulation of the planet. To obtain our final set of light curves, 
we sorted the light curves in each group by the amplitude
of the signal and kept the first 25 in each of the first three groups in Sector 1
and the first 20 in the first group in Sector 2 for a total
of 75 and 20 light curves, respectively. We then computed an estimate of the
non-Sol d background flux from the cadences during which the planet was below
the edge of the sunshade and removed this baseline from the flux.
Finally, we median-normalized all light curves (as opposed to the min-max
normalization used for the classification).
Our final dataset consisted of 912,605 data points in total. 
A representative sample of these signals is shown in Figure~\ref{fig:data}.

>>>>

For each of the two sectors considered, we downloaded a random subsample of 
1,000 short-cadence light curve files corresponding to postage stamps located 
across the full \TESS field of view and extracted the background flux time 
series (\textsf{SAP\_BKG}) and corresponding uncertainties
(\textsf{SAP\_BKG\_ERR}) from each. 
Not all postage stamps are equally informative, since the desired signal from 
Sol d is inhomogeneously spread across the \TESS detectors and manifests itself
differently in different regions (see \S\ref{sec:systematics}). 
We down-selected our pool of 1,000 targets to 75 maximally useful background 
light curves from Sector 1 and 20 from Sector 2. 
This down-selection was done with several criteria in mind: each light curve 
should contain a significant signal from Sol d; they should be representative 
of the general background flux modulation seen across the \TESS cameras, rather 
than containing any truly localized signals from astrophysical background 
sources; and the sample as a whole should contain the full range of typical 
behaviors of background across the entire \TESS field of view. 
To accomplish this, we applied a categorization and outlier rejection scheme to the ensemble of light curves.
We interpolated all light curves in Sector 1 onto the same time
grid, masked all cadences with nonzero \textsf{QUALITY} flags, and masked
cadences during which Sol d was below the edge of the sunshade.
During this selection step only, we also normalized the light curves to the same min-max range.
We computed the median
flux at each cadence along with an estimate of the variance based on the
median absolute deviation (MAD) across all light curves.
For each light curve, we calculated a score $\chi^2$ equal to the sum of the squares of the
deviation from the median at each of the $N$ cadences, normalized by the variance.
We removed all light curves with $\chi^2 < N$ from the pool, placing
them in a separate group. We repeated these steps several times,
classifying light curves into four groups for Sector 1 and two groups for Sector 2. 
We found that this
procedure effectively grouped together light curves with similar features,
increasing in variation within each group from the first group (most homogeneous) 
to the last group (most heterogeneous). In practice, we found light curves
in all but the last group to be dominated by 
the signal of Sol d, while light
curves in the last group were dominated by signals other than the
periodic modulation of the planet. To obtain our final set of light curves, 
we sorted the light curves in each group by the amplitude
of the signal and kept the first 25 in each of the first three groups in Sector 1
and the first 20 in the first group in Sector 2 for a total
of 75 and 20 light curves, respectively. We then computed an estimate of the
non-Sol d background flux from the cadences during which the planet was below
the edge of the sunshade and removed this baseline from the flux.
Finally, we median-normalized all light curves (as opposed to the min-max
normalization used for the classification).
Our final dataset consisted of 912,605 data points in total. 
A representative sample of these signals is shown in Figure~\ref{fig:data}.
